Manuscript progress report

### 2023-11-30 Docs/manuscript.Rmd
meeting notes

---
title: "Manuscript progress report"
author: "Ying Jin"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: yes
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
---

@@

@@

```{r fig_pred}
rand_id <- sample(501:600, size = 4)
# range(pred_list_all[[1]]$pred0.2, na.rm = T)
fig_fgfpca <- pred_list_all[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time")

>>>>

---
title: "Manuscript progress report"
author: "Ying Jin"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: no
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
    keep_tex: true
---

@@

```{r fig_sim_data}
rand_id <- sample(501:600, size = 4)
pred_list_all[[1]] %>% filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  facet_wrap(~id)+
  labs(title = "Simulated data")
```

@@

```{r fig_pred}
# range(pred_list_all[[1]]$pred0.2, na.rm = T)
fig_fgfpca <- pred_list_all[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time")
